### 2013-10-04 Rcode/readme.rmd
added LogLik_conv to mix.R; fixed bugs related to LogLik not taking logs

```{r}
#install q value package, and load in ash code
source("../Rcode/ash.R")
beta.ash.all = ash(betahat,s)
beta.ash.good = ash(betahat[p$type=="GOOD"],s[p$type=="GOOD"])
plot(beta.ash.good$PosteriorMean,beta.ash.all$PosteriorMean[p$type=="GOOD"])
plot(beta.ash.good$PositiveProb,beta.ash.all$PositiveProb[p$type=="GOOD"])
```
So here it makes no difference whether you use all the observations or the just the good ones -
the noise is ignored (as it should be!)

@@

The following computes the log likelihood for the two fitted ash models,
first with $\beta \sim \sum_k \pi_k N(0,\sigma_k^2)$, and then $\beta_s \sim \sum_k \pi_k N(0, \sigma^2_k se^2_s)$:
```{r}
cat(mixseLoglik(hh.betahat,hh.ash$fitted.f$pi, hh.ash$fitted.f$mu, hh.ash$fitted.f$sigma, hh.sebetahat),mixseLoglik(hh.betahat,hh.ash2$fitted.f$pi, hh.ash2$fitted.f$mu, sqrt(hh.ash2$fitted.f$sigma^2+1), hh.sebetahat,FUN="*"))
```
Looks like the second model fits better.

@@

Another unexpected feature is that the ASH analysis based
on z scores is rather different from the standard q value analysis, even though they are both based on z scores.
Look:
```{r}
plot(as.numeric(hh.q$qvalue),hh.ash2$qval,cex=0.2,ylab="ASH q value",xlab="standard q value",main="ASH vs standard q value")
cat(hh.ash2$fitted.f$pi[1],hh.q$pi0)
```
At first I was really worried about this - the pi0 estimate
is much bigger using the p values. However, this is all to
do with the assumptions. The q value approach estimates
pi0 by looking at the p values near 1. Effectively it assumes
that all the p values near 1 are null. At first this seems OK.
But note that it actually corresponds to assuming that all the z scores near 0 are null - that is, you can never see a z score of 0 under the alternative. In contrast we assume that the distribution of z scores under the alternative also has its mode at 0 - under this assumption not all z scores near 0 will be null at all.... these are very different assumptions. 
(Of course, z scores near 0 won't give "significant"" results in either approach.)

@@

mixseLoglik(bhat.test,test1.ash1$fitted.f$pi,test1.ash1$fitted.f$mu,test1.ash1$fitted.f$sigma,hh.sebetahat)
mixseLoglik(bhat.test,test1.ash2$fitted.f$pi,test1.ash2$fitted.f$mu,sqrt(test1.ash2$fitted.f$sigma^2+1),hh.sebetahat,FUN="*")

mixseLoglik(bhat2.test,test2.ash1$fitted.f$pi,test2.ash1$fitted.f$mu,test2.ash1$fitted.f$sigma,hh.sebetahat)
mixseLoglik(bhat2.test,test2.ash2$fitted.f$pi,test2.ash2$fitted.f$mu,sqrt(test2.ash2$fitted.f$sigma^2+1),hh.sebetahat,FUN="*")
```

>>>>

```{r}
#install q value package, and load in ash code
source("../Rcode/ash.R")
source("../Rcode/ash.oldfuncs.R")
beta.ash.all = ash(betahat,s)
beta.ash.good = ash(betahat[p$type=="GOOD"],s[p$type=="GOOD"])
plot(beta.ash.good$PosteriorMean,beta.ash.all$PosteriorMean[p$type=="GOOD"])
plot(beta.ash.good$PositiveProb,beta.ash.all$PositiveProb[p$type=="GOOD"])
```
So here it makes no difference whether you use all the observations or the just the good ones -
the noise is ignored (as it should be!)

@@

The following computes the log likelihood for the two fitted ash models,
first with $\beta \sim \sum_k \pi_k N(0,\sigma_k^2)$, and then $\beta_s \sim \sum_k \pi_k N(0, \sigma^2_k se^2_s)$:
```{r}
cat(LogLik_conv(hh.ash$fitted.g, hh.betahat, hh.sebetahat),mixseLoglik(hh.betahat,hh.ash$fitted.g$pi, hh.ash$fitted.g$mean, hh.ash$fitted.g$sd, hh.sebetahat),mixseLoglik(hh.betahat,hh.ash2$fitted.g$pi, hh.ash2$fitted.g$mean, sqrt(hh.ash2$fitted.g$sd^2+1), hh.sebetahat,FUN="*"))
```
Looks like the second model fits better.

@@

Another unexpected feature is that the ASH analysis based
on z scores is rather different from the standard q value analysis, even though they are both based on z scores.
Look:
```{r}
plot(as.numeric(hh.q$qvalue),hh.ash2$qval,cex=0.2,ylab="ASH q value",xlab="standard q value",main="ASH vs standard q value")
cat(hh.ash2$fitted.g$pi[1],hh.q$pi0)
```
At first I was really worried about this - the pi0 estimate
is much bigger using the p values. However, this is all to
do with the assumptions. The q value approach estimates
pi0 by looking at the p values near 1. Effectively it assumes
that all the p values near 1 are null. At first this seems OK.
But note that it actually corresponds to assuming that all the z scores near 0 are null - that is, you can never see a z score of 0 under the alternative. In contrast we assume that the distribution of z scores under the alternative also has its mode at 0 - under this assumption not all z scores near 0 will be null at all.... these are very different assumptions. 
(Of course, z scores near 0 won't give "significant"" results in either approach.)

@@

mixseLoglik(bhat.test,test1.ash1$fitted.g$pi,test1.ash1$fitted.g$mean,test1.ash1$fitted.g$sd,hh.sebetahat)
mixseLoglik(bhat.test,test1.ash2$fitted.g$pi,test1.ash2$fitted.g$mean,sqrt(test1.ash2$fitted.g$sd^2+1),hh.sebetahat,FUN="*")

mixseLoglik(bhat2.test,test2.ash1$fitted.g$pi,test2.ash1$fitted.g$mean,test2.ash1$fitted.g$sd,hh.sebetahat)
mixseLoglik(bhat2.test,test2.ash2$fitted.g$pi,test2.ash2$fitted.g$mean,sqrt(test2.ash2$fitted.g$sd^2+1),hh.sebetahat,FUN="*")
```
